### 2016-07-26 notions.tex
slight change to correctness experiment

\heading{Relationships among notions.}
If we allow for trivial schemes, e.g. $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.\tsnote{In general, it isn't clear how to reduce correctness to the Priv notion.  In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the adversary expects~$(M,\aux)$ as input.}
Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).
\tsnote{Reducing correctness to the weaker version, wPriv, is syntactically possible, but not clear how to connect the success events.  In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?  Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.  Then the correctness attacker does what?  Ask some query~$q_z$ related to~$z$ (remember, queries are not syntactically restricted to set membership!) and see if the oracle returns the true value $q_z(S)$?  This is pretty complicated... Note that any query~$q$ the one-wayness adversary asks can be checked locally against the true value~$q(S)$ by the correctness adversary.  But still, it's not clear how to do a quality reduction.  }

>>>>

\heading{Relationships among notions.}
If we allow for trivial schemes, e.g. $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.\tsnote{In general, it isn't clear how to reduce correctness to the Priv notion.  In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the adversary expects~$(M,\aux)$ as input.}
Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).
\tsnote{Reducing correctness to the weaker version, wPriv, is syntactically possible, but not clear how to connect the success events.  In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?  Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.  Then the correctness attacker does what?  Ask some query~$q_z$ related to~$z$ ---remember, queries are not syntactically restricted to set membership!--- and see if the oracle returns the true value $q_z(S)$?  This is pretty complicated... and it's not clear how to do a quality reduction.   }
